---
output: ioslides_presentation
---

```{r include=F}
library(png)
library(grid)
library(knitr)

opts_chunk$set(echo=FALSE,
               warning=FALSE,
               message=FALSE,
               fig.width= 5,
               fig.height= 5,
               fig.align='center')

```






## Reproducible Research

```{r fig.height=4}
img <- readPNG("Images/Irreproducible.png")
 grid.raster(img)
```


<center>
Lewis Spurgin

EGI meeting, February 2016
</center>





## A reproducibility crisis?

```{r}
img <- readPNG("Images/Reinhart.png")
 grid.raster(img)
```





## A reproducibility crisis?

<div class="columns-2">

```{r fig.width=4}
img <- readPNG("Images/Reinhart.png")
 grid.raster(img)
```

<br>
"In their Excel spreadsheet, Reinhart and Rogoff had not selected the entire row when averaging growth figures: they omitted data from Australia, Austria, Belgium, Canada and Denmark... "

</div>






## A reproducibility crisis?

<div class="columns-2">

```{r fig.width=4}
img <- readPNG("Images/Reinhart.png")
 grid.raster(img)
```

<br>
"For an economist, the five most terrifying words in the English language are: I can't replicate your results. But for economists Carmen Reinhart and Ken Rogoff of Harvard, there are seven even more terrifying ones: I think you made an Excel error."

</div>







## A reproducibility crisis?

```{r fig.width=6,fig.height=4}
img <- readPNG("Images/News.png")
 grid.raster(img)
```




## Reproducibility and replicability
<br>
<br>

* **Replicability** is the ability to replicate results after completely performing an experiment again from scratch.

* **Reproducibility** is the ability to reproduce the same results from a dataset that has already been generated.









## Requirements for reproducible research
<br>
<br>

* Data are available

* Methods/analyses are transparent







## Data availability

* Now a requirement for many journals and funding agencies
* Gets you more citations
* Long-term storage of data

<br>

```{r fig.width=6,fig.height=2}
img <- readPNG("Images/Dryad.png")
 grid.raster(img)
```





## Data availability

* Usually tidied data uploaded
* What has been done to the raw data?
* Any possibility of errors?

<br>

```{r fig.width=6,fig.height=2}
img <- readPNG("Images/Dryad.png")
 grid.raster(img)
```





## Transparency in methods/analysis

* How were the data formatted?
  
* How were the data cleaned?
  
* What exploratory analyses were done?

* How did you create your final analyses/figures?





